Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-06-03 Masterarbeit_Robotik_Pamuk.tex
max_latency

\clearpage
\section{Xenomai}
\noindent Xenomai 3 is a real-time framework that offers two paths to real-time performance. The first approach supplements the Linux kernel with a compact real-time core dubbed Cobalt, demonstrated in Figure \ref{fig:cobalt}. Cobalt runs side-by-side with Linux, but it handles all time-critical activities like interrupt processing and real-time thread scheduling with higher priority than the regular kernel activities.

@@

\begin{table}[h]
	\centering
	\caption{Latency Statistics default in microseconds}
	\label{tab:x}
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (in \textmu s)} \\\hline
	Average Latency & 174.5us \\\hline
	Maximum Latency & 4070.02us \\\hline
	Minimum Latency & 6.96us \\\hline
	Standard Deviation & 359.27us \\\hline
	\end{tabular}
	\end{table}

>>>>

\clearpage
\section{Xenomai}
\noindent Xenomai 3 \cite{XenomaiXenomai} is a real-time framework that offers two paths to real-time performance. The first approach supplements the Linux kernel with a compact real-time core dubbed Cobalt, demonstrated in Figure \ref{fig:cobalt}. Cobalt runs side-by-side with Linux, but it handles all time-critical activities like interrupt processing and real-time thread scheduling with higher priority than the regular kernel activities.

@@

\begin{table}[h]
	\centering
	\caption{Latency Statistics default in microseconds}
	\label{tab:x}
	\begin{tabular}{|c|c|}\hline
	\textbf{Statistic} & \textbf{Value (in \textmu s)} \\\hline
	Average Latency & 46.22us \\\hline
	Maximum Latency & 707.62us \\\hline
	Minimum Latency & 15.59us \\\hline
	Standard Deviation & 52.13us \\\hline
	\end{tabular}
	\end{table}
\clearpage
